Article data analysis 2

### 2019-03-28 notebooks/article_notebook2.Rmd
changed x-axis on barplot figure

mut_report %>%
    left_join(isolate_data, by = "id") %>%
    gather(key, value, gene_names) %>%
    group_by(key, value, species) %>%
    dplyr::count() %>%
    ungroup() %>%
    mutate(value = if_else(value == 1, "Present", "Absent")) %>%
    spread(value, n, fill = 0) %>%
    rowwise() %>%
    mutate(
      Total = Present + Absent,
      Percent = round(Present / Total * 100, 1),
      lwr = round(get_binCI(Present, Total)[1], 1),
      upr = round(get_binCI(Present, Total)[2], 1)
    ) %>%
    mutate(species = factor(species,
                            levels = c("Broiler","Pig","Wild bird","Red fox")),
           key = paste0(toupper(substr(key, 1, 1)),
                        substr(key, 2, nchar(key))),
           group = if_else(key %in% c("GyrA","GyrB","ParC","ParE"), 1, 2)) %>%
  ggplot(aes(key, Percent, fill = species)) +
    geom_col(color = "black",
             position = position_dodge(1)) +
    geom_errorbar(
      aes(ymin = lwr, ymax = upr),
      width = 0.6,
      position = position_dodge(1)
    ) +
    scale_fill_manual(values = palette) +
    scale_x_discrete(labels = c("GyrA","GyrB","ParC","ParE",
                                "MarA","MarR","SoxR","RpoB",
                                "RobA")) +
    labs(y = "Percent (%) of isolates") +
    guides(fill = FALSE) +
    theme_classic() +
    theme(
      axis.text.x = element_text(
        angle = 90,
        size = 12,
        hjust = 1,
        vjust = 0.4
      ),
      axis.title.x = element_blank(),
      axis.text.y = element_text(size = 12),
      axis.title.y = element_text(size = 14),
      strip.text = element_text(size = 12)
    ) +
    facet_wrap(~ species)
```

>>>>

mut_report %>%
    left_join(isolate_data, by = "id") %>%
    gather(key, value, gene_names) %>%
    group_by(key, value, species) %>%
    dplyr::count() %>%
    ungroup() %>%
    mutate(value = if_else(value == 1, "Present", "Absent")) %>%
    spread(value, n, fill = 0) %>%
    rowwise() %>%
    mutate(
      Total = Present + Absent,
      Percent = round(Present / Total * 100, 1),
      lwr = round(get_binCI(Present, Total)[1], 1),
      upr = round(get_binCI(Present, Total)[2], 1)
    ) %>%
    mutate(species = factor(species,
                            levels = c("Broiler","Pig","Wild bird","Red fox")),
           key = paste0(toupper(substr(key, 1, 1)),
                        substr(key, 2, nchar(key))),
           group = if_else(key %in% c("GyrA","GyrB","ParC","ParE"), 1, 2)) %>%
  ggplot(aes(key, Percent, fill = species)) +
    geom_col(color = "black",
             position = position_dodge(1)) +
    geom_errorbar(
      aes(ymin = lwr, ymax = upr),
      width = 0.6,
      position = position_dodge(1)
    ) +
    scale_fill_manual(values = palette) +
    scale_x_discrete(limits = c("GyrA","GyrB","ParC","ParE",
                                "MarA","MarR","SoxR","RpoB",
                                "RobA")) +
    labs(y = "Percent (%) of isolates") +
    guides(fill = FALSE) +
    theme_classic() +
    theme(
      axis.text.x = element_text(
        angle = 90,
        size = 12,
        hjust = 1,
        vjust = 0.4
      ),
      axis.title.x = element_blank(),
      axis.text.y = element_text(size = 12),
      axis.title.y = element_text(size = 14),
      strip.text = element_text(size = 12)
    ) +
    facet_wrap(~ species)
```
